\vspace{1.0cm} \LARGE \bf fluB

### 2013-10-24 fluB.tex
Adding extra provisional plots.
Adding plots of pairwise tree-to-tree comparisons: normalized SPR and
mean delta TMRCA.
Also adding MDS plot with segments, where distances are proportion of
site pairs that show LD>0.5 (i.e. of the included heatmap).

>>>>

\subsection*{All segments reassort equally but some are more equal than others}
(comment - normalized approximate SPR distance plot suggests that all segments reassort to the same extent, but the mean \Delta TMRCA plot suggests that some segment pairs occassionally have TMRCAs similar to themselves i.e. only short-evolutionary-distance reassortments are observed)
(comment - also Sam expected that MP and NA would come out the way they did)
